A Technique for Inter-Retailer Recommendations

### 2014-06-12 paper2/paper.tex
Tweak abstract

\section*{Abstract}
\emph{The problem of making recommendations across retailers using only publicly
available information is explored. Experiments are conducted using real data in
which several recommender algorithms are compared. A novel latent feature
inter-retailer recommender system that leverages public intra-retailer
recommendation information is described and shown to outperform a nontrivial
content-based approach.}

@@

\begin{table}
\begin{center}
\begin{tabular}{ | l || c | c | c || c | c | c |}
\hline
Recommender & Precision & Recall & F1 Score & 2-Precision & 2-Recall & 2-F1 Score \\ \hline\hline
$Random$ & .002 & .001 & .001 & .021 & .008 & .012 \\ \hline
$Popularity$ & .016 & .019 & .017 & .080 & .096 & .087 \\ \hline
$RandomMap$ & .014 & .019 & .016 & .070 & .095 & .081 \\ \hline
$OneModel$ & .103 & .132 & .116 & .404 & .410 & .407 \\ \hline
$ContentBased$ & .014 & .020 & .016 &
\textbf{.115} & \textbf{.186} & \textbf{.142} \\ \hline 
$Neighborhood$ & .040 & .060 & .048 &
\textbf{.137} & \textbf{.240} & \textbf{.175} \\ \hline 
$LatentFeature$ & .036 & .060 & .045 &
\textbf{.174} & \textbf{.228} & \textbf{.197} \\ \hline
\end{tabular}
\caption{The performance of each of the recommenders across all categories. The
first five are the baseline recommenders outlined in the previous section. The
final three are the recommenders of interest, described in the Recommender
Algorithms section. The scores in bold are the most important results and are 
further illustrated in the following figure.}
\end{center}
\end{table}
\begin{figure}[!htbp]
    \centering
    \includegraphics[width=0.65\textwidth]{RecommenderPerformance2.png}
	\caption{The performance of the three main recommenders in terms of
    2-metrics across all categories. We emphasize the 2-F1 Score as our most
    important single metric of comparison. We see that the $LatentFeatureRecommender$
    outperforms the other recommenders in this score.} 
    \label{fig:RecommenderPerformance} 
\end{figure}
\pagebreak
\section*{Conclusion}
In this study, we address the problem of determining inter-retailer, or
inter-catalogue, item-item associations. We frame this problem as a recommender
problem, which motivates a relatively straightforward experiment in which a
candidate algorithm must connect two recommendation graphs by guessing edges
between them.

>>>>

\section*{Abstract}
\emph{The problem of making recommendation across retailers using only publicly
available information is explored. Several inter-retailer recommender algortihms
are presented. Each is compared in an experiment conducted with real data. A 
novel latent feature recommender that leverages public intra-retailer
recommendation information is described and shown to outperform a nontrivial
content-based approach.}

@@

\begin{table}
\begin{center}
\begin{tabular}{ | l || c | c | c || c | c | c |}
\hline
Recommender & Precision & Recall & F1 Score & 2-Precision & 2-Recall & 2-F1 Score \\ \hline\hline
$Random$ & .002 & .001 & .001 & .021 & .008 & .012 \\ \hline
$Popularity$ & .016 & .019 & .017 & .080 & .096 & .087 \\ \hline
$RandomMap$ & .014 & .019 & .016 & .070 & .095 & .081 \\ \hline
$OneModel$ & .103 & .132 & .116 & .404 & .410 & .407 \\ \hline
$ContentBased$ & .014 & .020 & .016 &
\textbf{.115} & \textbf{.186} & \textbf{.142} \\ \hline 
$Neighborhood$ & .040 & .060 & .048 &
\textbf{.137} & \textbf{.240} & \textbf{.175} \\ \hline 
$LatentFeature$ & .036 & .060 & .045 &
\textbf{.174} & \textbf{.228} & \textbf{.197} \\ \hline
\end{tabular}
\caption{The performance of each of the recommenders across all categories. The
first five are the baseline recommenders outlined in the previous section. The
final three are the recommenders of interest, described in the Recommender
Algorithms section. The scores in bold are the most important results and are 
further illustrated in the following figure.}
\end{center}
\end{table}
\begin{figure}[!htbp]
    \centering
    \includegraphics[width=0.75\textwidth]{RecommenderPerformance2.png}
	\caption{The performance of the three main recommenders in terms of
    2-metrics across all categories. We emphasize the 2-F1 Score as our most
    important single metric of comparison. We see that the $LatentFeatureRecommender$
    outperforms the other recommenders in this score.} 
    \label{fig:RecommenderPerformance} 
\end{figure}
\pagebreak
\section*{Conclusion}
In this study, we address the problem of determining inter-retailer, or
inter-catalogue, item-item associations. We frame this problem as a recommender
problem, which motivates a relatively straightforward experiment in which a
candidate algorithm must connect two recommendation graphs by guessing edges
between them.
